Predicting US Presidential Elections

### 2024-11-04 paper/paper.qmd
updated limitations

This model also does not take into consideration swing states and only uses them as categorical variables. This was done by design at this risk of overfitting.

>>>>

This model also does not take into consideration swing states and only uses them as categorical variables. This was done by design at this risk of overfitting. 
Further, the shy voter phenomenon may stop people from accurately reflecting their voter sentiment in the polls that our data is extracted from. For example, people voting for Donald Trump may feel that they will be ostracized for their choices and so, they may lie about their voting preferences by claiming to vote for Harris or say they’re undecided. Similarly, voters who do not wish to vote for Kamala Harris due to her policies but do not wish to vote for Trump either, specifically in swing states, are increasingly engaging in vote swapping mechanisms where they make deals with people in guaranteed blue states such that a blue state voter votes for an independent party while a swing state voter votes for Harris to ensure a Democratic win over Trump. This is an uninformed and non regulated practice which impedes the data we have and leads to inaccurate predictions.
